Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Change comments, so that it is clear who said what
This works better, if three people work on the paper.

\emph{IMPORTANT: @sol has to release a new version of hspec, that
includes the Specs-to-Spec and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

%% \begin{quote}
%%     @kazu: We e.g. say ill-behaved Monoid instance.  So is
%%     ``behavior'' really a bad word?  But I agree that some people in
%%     the community might associated it with something imperative.

@@

TBD(@sol): how to obtain evidence from Haddock markup.
Old version uses Haddock API but now uses GHC API directly. Why?

TBD(@sol): escape from HUnit. Why?

TBD(@sol): Old version executes one GHCi for each function examples.
But new version executes one GHCI per module.
Drastic speed up. Do We need a graph for execution time?

@@

\begin{quote}
@kazu: Can we use \verb|reverse| instead of \verb|rev| here?
\end{quote}

\begin{quote}
@sol: I used \verb|rev| just because it is short.
Actually I used \verb|reverse| once but it is overflowed
in the right hand side.
\end{quote}

@@

\begin{quote}
    TBD: @kazu: Do we need this to make our case?  I'm asking, because
    it will require some work to get the language right.

@@

@@

        @kazu: Do you think we should discuss this; or is it safe to
        ignore.

        @sol: Let's add this.

>>>>

\emph{IMPORTANT: sol: I have to release a new version of hspec, that
includes the Specs-to-Spec and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

%% \begin{quote}
%%     sol: We e.g. say ill-behaved Monoid instance.  So is
%%     ``behavior'' really a bad word?  But I agree that some people in
%%     the community might associated it with something imperative.

@@

TBD: kazu: how to obtain evidence from Haddock markup.
Old version uses Haddock API but now uses GHC API directly. Why?

TBD: kazu: escape from HUnit. Why?

TBD: kazu: Old version executes one GHCi for each function examples.
But new version executes one GHCI per module.
Drastic speed up. Do We need a graph for execution time?

@@

\begin{quote}
sol: Can we use \verb|reverse| instead of \verb|rev| here?
\end{quote}

\begin{quote}
kazu: I used \verb|rev| just because it is short.
Actually I used \verb|reverse| once but it is overflowed
in the right hand side.
\end{quote}

@@

\begin{quote}
    TBD: sol: Do we need this to make our case?  I'm asking, because
    it will require some work to get the language right.

@@

\begin{quote}
    sol: I think you can have several files with tests, but you have
    to combine the test suites manually.
\end{quote}

@@

        sol: Do you think we should discuss this; or is it safe to
        ignore.

        kazu: Let's add this.
